User guide -- microxanox R Package for microbial oxic and anoxic ecosystem simulations

### 2021-04-15 various_stuff/dev_vignettes/User-guide.Rmd
partial reproduction vignette code and data added

---
title: "User manual -- microxanox R Package for microbial oxic and anoxic ecosystem simulations"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{User manual -- microxanox R Package for microbial oxic and anoxic ecosystem simulations}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

>>>>

---
title: "User guide -- microxanox R Package for microbial oxic and anoxic ecosystem simulations"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{User guide -- microxanox R Package for microbial oxic and anoxic ecosystem simulations}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
